
\begin{frame}{Introduction}
  \begin{quote}
    Don't listen to his words, examine his achievements. \\-- Albert Einstein
  \end{quote}
  Theoretical physics is shaped not just by logic, but by creative principles
  guided by experience.
\end{frame}

\begin{frame}{Reason and Experience}
  \begin{itemize}
    \item Knowledge starts and ends with experience.
    \item Reason structures the system; experience validates it.
    \item Parallel with Euclidean geometry: axioms vs. empirical content.
  \end{itemize}
\end{frame}

\begin{frame}{Invention vs. Derivation}
  \begin{itemize}
    \item Basic laws are not derivable from experience.
    \item They are free inventions of the human mind.
    \item Goal: simplest possible basis that still fits all phenomena.
  \end{itemize}
\end{frame}

\begin{frame}{Development of Theoretical Method}
  \begin{itemize}
    \item Greece: pure logical systems.
    \item Galileo: experience as foundation of knowledge.
    \item Newton: uneasy balance between empirical and absolute concepts.
  \end{itemize}
\end{frame}

\begin{frame}{Theory and Reality}
  \begin{itemize}
    \item Theories must match experience, not derive from it.
    \item Relativity shows multiple conceptual bases can fit reality.
    \item Logical derivation alone is insufficient.
  \end{itemize}
\end{frame}

\begin{frame}{The Role of Mathematics}
  \begin{itemize}
    \item Mathematics enables discovery of physical laws.
    \item Simplicity and elegance are guiding principles.
    \item Mathematical constructs precede empirical verification.
  \end{itemize}
\end{frame}

\begin{frame}{Examples: General Theory}
  \begin{itemize}
    \item Riemannian metric \(\Rightarrow\) Einstein's field equations.
    \item Antisymmetric tensor \(\Rightarrow\) Maxwell equations.
    \item Spinor field \(\Rightarrow\) Dirac's electron theory.
  \end{itemize}
\end{frame}

\begin{frame}{Quantum Theory and Atomism}
  \begin{itemize}
    \item Born's interpretation: probability, not representation.
    \item Heisenberg: no absolute localization.
    \item Continuum theory can still imply atomism via integrals.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Theoretical physics is a fusion of thought and reality.
    \item Mathematics is the creative core, experience the judge.
    \item Future theories must unify depth with simplicity.
  \end{itemize}
\end{frame}
